---
title: "Simulate the Basic Solow Growth Model"
output:
  html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{BS}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Working Code Example
```{r, eval = F}
library(SolowVariants)
library(tidyverse)
theme_set(theme_bw())

# Setting up the parameter grid ---------------------------------
aux_np <- 200
aux_parameter_grid <-
  create_parameter_grid(
    c("B", "alpha", "delta", "n", "s"),
    c(10, 1 / 3, 0.1, 0.005, 0.22),
    c(NA, NA, NA, NA, NA),
    c(NA, NA, NA, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(K = 1, L = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation <- SimulateBasicSolowModel(aux_parameter_grid, aux_np,aux_startvalues)

# Visualise some variables ---------------------------------
VisualiseSimulation(aux_simulation,
                    c("YpW", "Y", "KpW"), 
                    "free")
```

## Elaboration
Parameters defining the BS
* TFP ($B$)
* Alpha ($\alpha$)
* Rate of capital depreciation ($\delta$)
* Population growth rate ($n$)
* Savings rate ($s$)
Remark: Those parameters can be found via the command: \code{getRequiredParams("BS")}.

Starting value of endogenous variables defining the BS
* Starting value of physical capital ($K_0$)
* Starting value of the labor force ($L_0$)
Remark: Those parameters can be found via the command: \code{getRequiredStartingValues("BS")}.

## Structural Equations to the Basic Solow Growth Model
$$
\begin{aligned}
Y_t &= BK_t^\alpha L_t^{1-\alpha} \\
r_t &= \alpha B \left(\frac{K_t}{L_t}\right)^{\alpha -1}\\
w_t &= (1-\alpha) \left(\frac{K_t}{L_t}\right)^\alpha \\
S_t &= sY_t \\
K_{t+1}&= sY_t + (1-\delta)K_t \\
L_{t+1}&=(1+n)L_t
\end{aligned}
$$
