---
title: "Simulate the Extended Solow Model with (semi- and fully) Endogenous Growth"
output:
  html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ESEG}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Working Code Example
```{r, eval = F}
library(SolowVariants)
theme_set(theme_bw())

# Setting up the parameter grid ---------------------------------
aux_np <- 200
aux_parameter_grid <-
  create_parameter_grid(
    c("alpha", "phi", "delta", "n", "s"),
    c(1 / 3, 0.99, 0.15, 0, 0.22),
    c(NA, NA, NA, NA, NA),
    c(NA, NA, NA, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(K = 1, L = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation <-
    SimulateExtendedSolowModelEndogenousGrowth(aux_parameter_grid,
                                               aux_np,
                                               aux_startvalues
    )
# Visualise some variables ---------------------------------
VisualiseSimulation(
  aux_simulation,
  c("gYpW", "gKpW"),
  "free"
)

# Economy in SS in the End ---------------------------------
steadystate_checker(aux_simulation, aux_parameter_grid, "ESEG")

```

## Elaboration
Parameters defining the ESEG

* Alpha ($\alpha$)
* Phi ($\phi$)
* Rate of capital depreciation ($\delta$)
* Population growth rate ($n$)
* Savings rate ($s$)

Remark: Those parameters can be found via the command: `getRequiredParams("BS")`.

Starting value of endogenous variables defining the BS

* Starting value of physical capital ($K_0$)
* Starting value of the labor force ($L_0$)

Remark: Those parameters can be found via the command: `getRequiredStartingValues("BS")`.

## Structural Equations to the Extended Solow Model with
### a) Semi-Endogenous Growth
$$\begin{aligned}
Y_t &= K_t^\alpha (AL_t)^{1-\alpha} \\
A_t &= K_t^\phi \\
K_{t+1}&= sY_t + (1-\delta)K_t \\
L_{t+1}&=(1+n)L_t \\
\end{aligned}$$

### b) Fully Endogenous Growth

$$\begin{aligned}
Y_t &= AK_t : A = L^{(1- \alpha)}\\
K_{t+1}&= sY_t + (1-\delta)K_t \\
L_{t+1}&=(1+n)L_t \quad \text{ where } n = 0 
\end{aligned}$$
