---
title: "Simulate the Extended Solow Growth Model with Human Capital"
output:
  html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ESHC}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Working Code Example
```{r, eval = F}
library(SolowVariants)
theme_set(theme_bw())

# Setting up the parameter grid ---------------------------------
aux_np <- 200
aux_parameter_grid <-
  create_parameter_grid(
    c("alpha", "phi", "n", "g", "sK", "sH", "delta"),
    c(1 / 3, 1 / 3, 0.005, 0.02, 0.15, 0.15, 0.2),
    c(NA, NA, NA, NA, NA, NA, NA),
    c(NA, NA, NA, NA, NA, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(A = 1, K = 1, L = 1, H = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation <- SimulateExtendedSolowModelHumanCapital(aux_parameter_grid, aux_np,aux_startvalues)

# Visualise some variables ---------------------------------
VisualiseSimulation(aux_simulation,
                    c("YpW", "KpEW", "HpEW"), 
                    "free")

# Verify whether the economy is 'in' steady state in the final period ---------------------------------

steadystate_checker(aux_simulation, aux_parameter_grid, "ESHC")

```

## Elaboration
Parameters defining the ESHC

* Alpha ($\alpha$)
* Phi ($\phi$)
* Population growth rate ($n$)
* Growth rate of total factor productivity ($g$)
* Savings rate to human capital ($sK$)
* Savings rate to physical capital ($sH$)
* Rate of capital depreciation ($\delta$)

Remark: Those parameters can be found via the command: `getRequiredParams("ESHC")`.

Starting value of endogenous variables defining the ESHC

* Starting value of total factor productivity ($A_0$)
* Starting value of the labor force ($L_0$)
* Starting value of human capital ($H_0$)
* Starting value of physical capital ($K_0$)

Remark: Those parameters can be found via the command: `getRequiredStartingValues("ESHC")`.

## Structural Equations to the Extended Solow Growth Model with Human Capital
$$
\begin{aligned}
Y_t &= K_t^\alpha * H_t^\phi * (A_t * L_t)^{(1- \alpha - \phi)} \\
K_{t+1} &= s_KY_t + (1-\delta)K_{t} \\
H_{t+1} &= s_HY_t + (1-\delta)H_{t} \\
L_{t+1}&=(1+n)L_t \\
A_{t+1}&=(1+g)A_t \\
\end{aligned}
$$
