---
title: "Simulate the Extended Solow Growth Model for the Small Open Economy"
output:
  html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{ESSOE}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Working Code Example
```{r, eval = F}
library(SolowVariants)
library(tidyverse)
theme_set(theme_bw())

# Setting up the parameter grid ---------------------------------
aux_np <- 200
getRequiredParams("ESSOE")
getRequiredStartingValues("ESSOE")
aux_parameter_grid <-
  create_parameter_grid(
    c("B", "alpha", "n", "s", "r"),
    c(1, 1 / 3, 0.005, 0.2, 0.04),
    c(NA, NA, NA, NA, NA),
    c(NA, NA, NA, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(L = 1, V = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation <- SimulateExtendedSolowModelSmallOpenEconomy(aux_parameter_grid, aux_np,aux_startvalues)

# Visualise some variables ---------------------------------
VisualiseSimulation(aux_simulation,
                    c("YpW", "KpEW", "VpEW"), 
                    "free")

```

## Elaboration
Parameters defining the BS
* Total factor productivity ($B$)
* Alpha ($\alpha$)
* Population growth rate ($n$)
* Savings rate to physical capital ($s$)
* Real rate of return on capital ($r$)
Remark: Those parameters can be found via the command: \code{getRequiredParams("ESSOE")}.


Starting value of endogenous variables defining the BS
* Starting value of the labor force ($L_0$)
* Starting value of national wealth ($V_0$)
Remark: Those parameters can be found via the command: \code{getRequiredStartingValues("ESSOE")}.

## Structural Equations to the Extended Solow Growth Model for the Small Open Economy
$$
\begin{aligned}
Y_t &= BK_t^\alpha L_t^{1-\alpha} \\
Y_n &= Y_t + \bar{r}F_t \\
V_t &= K_t + F_t\\
r_t &= \alpha B \left(\frac{K_t}{L_t}\right)^{\alpha -1}\\
w_t &= (1-\alpha) B \left(\frac{K_t}{L_t}\right)^\alpha \\
S_t &= sY_t \\
S_t &= V_{t+1} - V_t\\
L_{t+1}&=(1+n)L_t \\
\end{aligned}
$$
