---
title: "SolowVariants"
output:
  html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{SolowVariants}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  dev = "png"
)
```

## What does this package provide?
1. functions to simulate the following Solow growth models
    - Basic Solow Growth Model
    - General Solow Growth Model
    - Extended Solow Growth Model with Human Capital
    - Extended Solow Growth Model for the Small and Open Economy
    - Extended Solow Growth Model with Scarce Resources
      - with Oil
      - with Land
      - with Oil and Land
    - Extended Solow Growth Model with Endogenous Technological Growth
      - version put forward by Romer
      - version put forward by Cozzi
2. function to nicely visualise certain variables of a simulation
3. function to visualise several simulations to compare them
    - Example 1: An increase parameter s in period 50 vs. a decrease in capital depreciation rate, $\delta$, in period 50.
    - Example 2: Compare output in the basic Solow growth model to Output in the general Solow growth model. (both with the same common parameters.)
    - Example 3: Compare the extended Solow growth models with land, a fixed scarce resource, and the the extended Solow growth models with oil, a not-fixed but depletable scarce resource.
    - and many more.

## Illustrative Examples
### Simulation of a Solow Variant
```{r, eval = F}
library(SolowVariants)
theme_set(theme_bw())

# Setting up the parameter grid ---------------------------------
aux_np <- 200
aux_parameter_grid <-
  create_parameter_grid(
    c("B", "alpha", "delta", "n", "s"),
    c(10, 1 / 3, 0.1, 0.005, 0.22),
    c(NA, NA, NA, NA, NA),
    c(NA, NA, NA, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(K = 1, L = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation <- SimulateBasicSolowModel(aux_parameter_grid, aux_np,aux_startvalues)

# Visualise some variables ---------------------------------
VisualiseSimulation(aux_simulation,
                    c("YpW", "Y", "KpW"), 
                    "free")

# Verify whether the economy is 'in' steady state in the final period ---------------------------------

steadystate_checker(aux_simulation, aux_parameter_grid, "BS")

```
### Comparison of different Solow Variants
```{r, eval = T, fig.width = 7, fig.height = 4.8, fig.align='center'}
suppressPackageStartupMessages(library(SolowVariants))
aux_np <- 200

aux_parameter_grid <-
  create_parameter_grid(
    c("B", "alpha", "delta", "n", "s"),
    c(10, 1 / 3, 0.1, 0.005, 0.22),
    c(NA, NA, 100, NA, NA),
    c(NA, NA, 0.05, NA, NA),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux_startvalues <- list(K = 1, L = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation_BS <- SimulateBasicSolowModel(aux_parameter_grid, aux_np, aux_startvalues)


aux2_parameter_grid <-
  create_parameter_grid(
    c("g", "alpha", "delta", "n", "s"),
    c(0.05, 1 / 3, 0.1, 0.005, 0.22),
    c(NA, NA, NA, NA, 50),
    c(NA, NA, NA, NA, 0.05),
    aux_np
  )

# Setting starting values for K and L ---------------------------------
aux2_startvalues <- list(A = 1, K = 1, L = 1)

# Simulate the basic Solow growth model ---------------------------------
aux_simulation_GS <- SimulateGeneralSolowModel(aux2_parameter_grid, aux_np, aux2_startvalues)

# Comparing the two economies (solow variants) ---------------------------------
compare_simulations(
  list(aux_simulation_BS, aux_simulation_GS), 
  c("BS", "GS"), c("logY", "gYpW", "YpEW", "RR")
)
```






## Simulation Functions
| Solow Variant                                                             | Simulation Function                                    |
|:------------------------------------------------------------------------- |:------------------------------------------------------ |
| Basic Solow Growth Model                                                  | `SimulateBasicSolowGrowthModel()`                      |
| General Solow Growth Model                                                | `SimulateGeneralSolowModel()`                          |
| Extended Solow Growth Model with Human Capital                            | `SimulateExtendedSolowModelHumanCapital()`             |
| Extended Solow Growth Model for the Small and Open Economy                | `SimulateExtendedSolowModelSmallOpenEconomy()`         |
| Extended Solow Growth Model with Scarce Resource Land                     | `SimulateExtendedSolowModelScarceResourceLand()`       |
| Extended Solow Growth Model with Scarce Resource Oil                      | `SimulateExtendedSolowModelScarceResourceOil()`        |
| Extended Solow Growth Model with Scarce Resources Oil *and* Land          | `SimulateExtendedSolowModelScarceResourceOilAndLand()` |
| Extended Solow Growth Model with Endogenous Technological Growth | `SimulateExtendedSolowModelEndogenousGrowth()`         |
| Extended Solow Growth Model with Endogenous Technological Growth by Romer | `SimulateExtendedSolowModelEndogenousGrowthRomer()`    |
| Extended Solow Growth Model with Endogenous Technological Growth by Cozzi (Romer Extension) | `SimulateExtendedSolowModelEndogenousGrowthCozziOne()`    |
| Extended Solow Growth Model with Endogenous Technological Growth by Cozzi (Hybrid Model) | `SimulateExtendedSolowModelEndogenousGrowthCozziTwo()`    |

## Model Abbreviations
The table below shows the used abbreviations, so-called model codes, that will be used throughout the package to refer to the respective Solow Growth Model Variants.

| Solow Variant                                                             | Simulation Function |
|:------------------------------------------------------------------------- |:------------------- |
| Basic Solow Growth Model                                                  | BS                  |
| General Solow Growth Model                                                | GS                  |
| Extended Solow Growth Model with Human Capital                            | ESHC                |
| Extended Solow Growth Model for the Small and Open Economy                | ESSOE               |
| Extended Solow Growth Model with Scarce Resource Land                     | ESSRL               |
| Extended Solow Growth Model with Scarce Resource Oil                      | ESSRO               |
| Extended Solow Growth Model with Scarce Resources Oil *and* Land          | ESSROL              |
| Extended Solow Growth Model with Endogenous Technological Growth by Romer | ESEGRomer           |
| Extended Solow Growth Model with Endogenous Technological Growth by Cozzi | ESEG                |

## Variable Abbreviations
| Full Variable Name                                        | Variable Abbreviation |
|:--------------------------------------------------------- |:---------------------:|
| "Total Factor Productivity"                               |         "TFP"         |
| "Human Capital Stock"                                     |          "H"          |
| "Log of Human Capital Stock"                              |        "logH"         |
| "Capital Stock"                                           |          "K"          |
| "Log of Capital Stock"                                    |        "logK"         |
| "Growth Rate of Capital Stock"                            |         "gK"          |
| "Growth Rate of Human Capital Stock"                      |         "gH"          |
| "Capital Stock per Worker"                                |         "KpW"         |
| "Log of Capital Stock per Worker"                         |       "logKpW"        |
| "Growth Rate of Capital Stock per Worker"                 |        "gKpW"         |
| "Human Capital Stock per Worker"                          |         "HpW"         |
| "Log of Human Capital Stock per Worker"                   |       "logHpW"        |
| "Growth Rate of Human Capital Stock per Worker"           |        "gHpW"         |
| "Capital Stock per Effective Worker"                      |        "KpEW"         |
| "Log of Capital Stock per Effective Worker"               |       "logKpEW"       |
| "Growth Rate of Capital Stock per Effective Worker"       |        "gKpEW"        |
| "Human Capital Stock per Effective Worker"                |        "HpEW"         |
| "Log of Human Capital Stock per Effective Worker"         |       "logHpEW"       |
| "Growth Rate of Human Capital Stock per Effective Worker" |        "gHpEW"        |
| "Labor Stock"                                             |          "L"          |
| "Wage Rate"                                               |         "WR"          |
| "Rental Rate"                                             |         "RR"          |
| "Capital Rental Rate"                                     |         "RR"          |
| "Land Rental Rate"                                        |         "LR"          |
| "Output"                                                  |          "Y"          |
| "Log of Output"                                           |        "logY"         |
| "Growth Rate of Output"                                   |         "gY"          |
| "Output per Worker"                                       |         "YpW"         |
| "Log of Output per Worker"                                |       "logYpW"        |
| "Growth Rate of Output per Worker"                        |        "gYpW"         |
| "Output per Effective Worker"                             |        "YpEW"         |
| "Log of Output per Effective Worker"                      |       "logYpEW"       |
| "Growth Rate of Output per Effective Worker"              |        "gYpEW"        |
| "National Output"                                         |         "Yn"          |
| "National Wealth"                                         |          "V"          |
| "National Wealth per Worker"                              |         "VpW"         |
| "Net Foreign Assets"                                      |          "F"          |
| "Net Foreign Assets per Worker"                           |         "FpW"         |
| "National Savings"                                        |         "Sn"          |
| "Energy Use"                                              |          "E"          |
| "Resource Stock"                                          |          "R"          |
| "Consumption"                                             |          "C"          |
| "Consumption per Worker"                                  |         "CpW"         |
| "Consumption per Effective Worker"                        |        "CpEW"         |
| "Capital to Output Ratio"                                 |         "CtO"         |

## Vignettes to each Solow Growth Model Variant
The following hyperlinks link directly to the vignettes that contain explanations on the respective Solow variant.

[BS](BS.html)

[GS](GS.html)

[ESSOE](ESSOE.html)

[ESHC](ESHC.html)

[ESSRO](ESSRO.html)

[ESSRL](ESSRL.html)

[ESSROL](ESSROL.html)

[ESEG](ESEG.html)

[ESEGRomer](ESEGRomer.html)

Remark: You can call any of these directly with, for example, `vignette("BS")`.


## Remark to you if you are new to R
- the example code throughout this package uses input assignment by position. see the example below.
- when it is unclear how to use a function, make use of the question mark, such as`?compare_simulations`.
- to get more information on the package and the model use the vignettes, `vignette("SolowVariants"); vignette("ESEG")`
Example regarding assignment by position 
```
f <- function(x, y){x + y}
f(x = 3, y = 3) # argument assignment by name
f(3, 3) # argument assignment by position
```
This is insofar relevant as the example code will use 